A decomposition based on constrained clustering algorithms for job shop scheduling problems\thanks{Supported by organization x.}

### 2021-09-22 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
Updating abstract

\begin{document}
%
\title{A decomposition based on constrained clustering algorithms for job shop scheduling problems\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{1}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{1,2}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{M. El-Kholany et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
\email{\{mohammed.el-kholany, konstantin.schekotihin and martin.gebser\}@aau.at}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
Technische Universität Graz, Graz, Austria\\
\email{mgebser@ist.tugraz.at}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Scheduling decision in production planning plays a significant role in the manufacturing industry. A good schedule may lead to solve production problems and improve productivity. Job-shop Scheduling Problem (JSP) is one of the most crucial problems in production systems. JSP deals with allocating tasks on resources and determining the sequence of the operations on each machine. The main objective of JSP is to complete the processing of all operations in a minimal time. One of the most effective approaches studied by many researchers for solving the JSP is decomposition. This work aims to apply the decomposition strategy to split the problem into a series of sub-problems using data mining methodologies. We will propose a clustering algorithm to group the data points (operations) into clusters, where each cluster is a Time Window. The decomposition process depends on two main phases; the first phase is to extract features to predict the sequence of the operations on each machine. These features are extracted either from the problem itself or from solutions obtained by other heuristics. The second phase is to develop a constrained clustering algorithm to assign each data object (an operation) into a cluster. We solved the problem using the Answer Set Programming model, and we tested our proposed algorithm on a set of benchmark instances, and the results showed that our proposed outperformed other heuristics in most cases. The results also showed that some features like \textit{Remaining Processing Time}, \textit{Machine Load} and \textit{Earliest starting Time} have a significant impact on the solution quality.

>>>>

\begin{document}
%
\title{A decomposition based on constrained clustering algorithms for job shop scheduling problems\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Mohammed M. S. El-Kholany\inst{1}\orcidID{0000-1111-2222-3333} \and
Second Author\inst{1}\orcidID{1111-2222-3333-4444} \and
Third Author\inst{1}\orcidID{2222--3333-4444-5555}}
%
\authorrunning{M. El-Kholany et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Alpen-Adria-Universität Klagenfurt, Klagenfurt, Austria 
\email{\{mohammed.el-kholany, konstantin.schekotihin and martin.gebser\}@aau.at}\\
%\url{http://www.springer.com/gp/computer-science/lncs} \and
Technische Universität Graz, Graz, Austria\\
\email{mgebser@ist.tugraz.at}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Scheduling decision in production planning plays a significant role in the manufacturing industry. A good schedule may lead to solve production problems and improve productivity. Job-shop Scheduling Problem (JSP) is one of the most crucial problems in production systems. JSP deals with allocating tasks on resources and determining the sequence of the operations on each machine while completing all tasks as early as possible. One of the most effective approaches studied by many researchers for solving the JSP is decomposition. This work investigates applying the decomposition strategy to split the problem into a series of sub-problems using data mining methodologies. This study proposes a constrained clustering algorithm to group the data objects (operations) into clusters, where each cluster is a Time Window. The decomposition process depends on two main phases; the first phase is to extract features to predict the sequence of the operations on each machine. These features are extracted either from the problem itself or from solutions obtained by other heuristics. The second phase is to develop a constrained clustering algorithm to assign each data object (an operation) into a cluster. We solved the problem using the Answer Set Programming model, and we tested our proposed algorithm on a set of benchmark instances, and the results showed that our proposed outperformed other heuristics in most cases. The results also showed that some features like \textit{Remaining Processing Time}, \textit{Machine Load} and \textit{Earliest starting Time} have a significant impact on the solution quality.
